Supplemental Materials for ``Universals of word order reflect optimization of grammars for efficient communication''

### 2019-10-25 writeup/pnas-word-order-si.tex
typo

Taken together, the order of the xcomp dependency tends to agree with that of most other \emph{xcomp} dependencies, with the sole exception of Gothic.
\end{enumerate}

>>>>

Taken together, the order of `want' and its complement tends to agree with that of most other \emph{xcomp} dependencies, with the sole exception of Gothic.
\end{enumerate}
